Stellar Bars in Isolated Gas-Rich Spiral Galaxies Do Not Slow Down

### 2023-04-21 paper/ms.tex
Further updates to previous simulation work

{\bf \citet{2013MNRAS.429.1949A, 2014MNRAS.438L..81A} find stable evolution in
\Rot{} for a triaxial halo over $10\,\textrm{Gyr}$ with initial (final) gas
fractions of $100\%$ ($7\%$), $75\%$ ($6\%$), and $50\%$ ($5\%$). For a model
with $20\%$ ($3\%$) gas fraction they find an increasing \Rot{}. In their model
with a spherical halo they always find increasing \Rot{}, contrary to the
present work. We note there is a structural difference in their dark matter
halo. They use a cored isothermal sphere as opposed to our Hernquist halo It is
not clear to us the impact this would have on the expected torque from the halo
(i.e., the velocity structure of their halo may allow for more efficient capture
and thus stronger torquing). These authors make no mention of the process by
which the halo braking process is arrested, as we propose in the present paper.
\textcolor{red}{Lars, Elena - I'm most worried about this paragraph. Is the
argument about cored isothermal sphere reasonable?} }

>>>>

{\bf \citet{2013MNRAS.429.1949A, 2014MNRAS.438L..81A} find stable evolution in
\Rot{} for a triaxial halo over $10\,\textrm{Gyr}$ with initial (final) gas
fractions of $100\%$ ($7\%$), $75\%$ ($6\%$), and $50\%$ ($5\%$). For a model
with $20\%$ ($3\%$) gas fraction they find an increasing \Rot{}. In their model
with a spherical halo they always find increasing \Rot{}, contrary to the
present work. We note there is a structural difference in their dark matter
halo. They use a cored isothermal sphere as opposed to our Hernquist halo It is
not clear to us the impact this would have on the expected torque from the halo
(i.e., the velocity structure of their halo may allow for more efficient capture
and thus stronger torquing). These authors make no mention of the process by
which the halo braking process is arrested, as we propose in the present paper.
\textcolor{red}{Lars, Elena - I'm most worried about this paragraph. Is the
argument about cored isothermal sphere reasonable? I'm unsure if the velocity
structure between a cored isothermal sphere and a Hernquist profile is really
different enough to matter.} }

{\bf There may also be issues related to structural differences between their
bars and the bar considered in this work. In our case, we allowed the bar to
form in an $N$-body run and then added gas after the bar formation. In
\citet{2013MNRAS.429.1949A, 2014MNRAS.438L..81A} the bar forms from a disk that
is initially gas-rich. Neither approach is inherently better, but it is known
that in the latter case the resultant bar strength is weaker for initially
gas-rich systems \citep[e.g.,][]{2013MNRAS.429.1949A}. Weaker bars should be
less efficient at driving gas inwards and thus experience less positive torque
from the gas phase. A direct comparison based on the torque by the gas phase on
the bar is necessary.}
